---
title: "WISN post analysis"
author: "Siddhesh"
date: "13/12/2020"
output: html_document
---
# Workforce problems at rural public health-centres in India: A WISN retrospective analysis and national-level modelling study
# ASAR

some post analysis

``````{r @Siddhesh}
#Get packages
library(geepack)
library(tidyverse)
library(ggplot2)
library(ggstatsplot)
library(broom)
library(doBy)
library(emmeans)
library(data.table)
library(stringr)
library(forcats)
library(GGally)
library(ggpubr)
library(cowplot)
library(pastecs)
library(ppcor)
library(corrplot)
library(yardstick)
library(DescTools)
```

``````{r RHS-WISN post-analysis @Siddhesh}
#Getting data
wisn.rhs <- read.csv("../analysis/data_RHS_WISN_comparision.csv")

#Some transformations
wisn.rhs$ST[wisn.rhs$ST == "Andhra Pradesh*"] <-"Andhra Pradesh"
wisn.rhs$ST[wisn.rhs$ST == "Telangana*"] <- "Telangana" 
wisn.states <- wisn.rhs[-c(37),]
wisn.india <- wisn.rhs %>%
  filter(ST == 'All India')
df.rhs <- wisn.rhs 

#Function for partial correlations 
pcor_panel_y <- function(data, mapping, ...) {
  ## remove x, y mapping
  grp_aes <- mapping[setdiff(names(mapping), c("x", "y"))]
  ## extract the columns to which x and y is mapped
  xy <- sapply(mapping[c("x", "y")], rlang::as_name)
  #Y#print(xy)
  ## calculate pcor per group
  stats_est <- data %>%
    group_modify(function(dat, grp) {
      res <- pcor(dat, method = 'spearman')$estimate %>%
        as_tibble() %>%
        setNames(names(dat)) ## needed b/c in pcor names are sometimes messed up
      res <- res %>%
        mutate(x = names(res)) %>%
        gather(y, v_est, -x)
      res %>%
        filter(x == xy[1], y == xy[2]) ## look only at the pcors of this panel
    }) %>%
    mutate(x = 1, y = seq_along(y))
  # -
  stats_p <- data %>%
    group_modify(function(dat, grp) {
      res <- pcor(dat, method = 'spearman')$p.value %>%
        as_tibble() %>%
        setNames(names(dat)) ## needed b/c in pcor names are sometimes messed up
      res <- res %>%
        mutate(x = names(res)) %>%
        gather(y, v_p, -x)
      res %>%
        filter(x == xy[1], y == xy[2]) ## look only at the pcors of this panel
    }) %>%
    mutate(x = 1, y = seq_along(y))
  # -
  stats_s <- data %>%
    group_modify(function(dat, grp) {
      res <- pcor(dat, method = 'spearman')$statistic %>%
        as_tibble() %>%
        setNames(names(dat)) ## needed b/c in pcor names are sometimes messed up
      res <- res %>%
        mutate(x = names(res)) %>%
        gather(y, v_stat, -x)
      res %>%
        filter(x == xy[1], y == xy[2]) ## look only at the pcors of this panel
    }) %>%
    mutate(x = 1, y = seq_along(y))
  # -
  #stats <- cbind(stats_est, stats_p)#, stats_s)
  stats <- stats_est %>% right_join(stats_p)
  print(stats)
  val_est <- paste("Ï (rho) = ",round(stats$v_est, 3))
  val_p <- paste("p = ",(format.pval(round(stats$v_p ,3), eps = .001, digits = 3)))
  #val_label <- paste(val_est, val_p, sep = "\n")
  #print(val_label)
  ggplot(stats, aes(x, y,
             label = paste(val_est, val_p, sep = "\n")
             )
         ) +
    geom_text(grp_aes) +
    ylim(range(stats$y) + c(-2, 2))
}


#PHC workload correlations
phc_wisn_states <- wisn.states %>%
  dplyr::select(NURSE_PHC_R_P_WISN_ratio, DOC_PHC_R_P_WISN_ratio) %>%
  rename('PHC-Nurses WISN Ratio' = NURSE_PHC_R_P_WISN_ratio, 
         'PHC-Doctors WISN Ratio' = DOC_PHC_R_P_WISN_ratio) %>%
  na.omit()

phc_wisn_ratio_corrs <- ggpairs(phc_wisn_states, 
                                upper = list(continuous = pcor_panel_y), 
                                diag = list(continuous = wrap(ggally_barDiag, binwidth = 0.04))) +
  theme_bw()

ggsave("../analysis/phc_wisn_ratio_corrs.png", phc_wisn_ratio_corrs, device = 'png', dpi = 300, width = 4, height = 4)

#CHC workload correlations
chc_wisn_states <- wisn.states %>%
  dplyr::select(NURSE_CHC_R_P_WISN_ratio, PAED_CHC_R_P_WISN_ratio, 
         OBGY_CHC_R_P_WISN_ratio, PHY_CHC_R_P_WISN_ratio,
         SUR_CHC_R_P_WISN_ratio, GDMO_AL_CHC_R_P_WISN_ratio) %>%
  rename('CHC-Nurses WISN Ratio' = NURSE_CHC_R_P_WISN_ratio, 
         'CHC-Paediatricians WISN Ratio' = PAED_CHC_R_P_WISN_ratio, 
         'CHC-OBGYNs WISN Ratio' = OBGY_CHC_R_P_WISN_ratio, 
         'CHC-Physicians WISN Ratio' = PHY_CHC_R_P_WISN_ratio, 
          'CHC-Surgeons WISN Ratio' = SUR_CHC_R_P_WISN_ratio,
          'CHC-GDMOs WISN Ratio' = GDMO_AL_CHC_R_P_WISN_ratio) %>%
  na.omit()

#Partial correlations
pcor_chc_wisn_ratio <- pcor(chc_wisn_states, method = 'spearman')

chc_wisn_ratio_corrs <- ggpairs(chc_wisn_states, 
                                upper = list(continuous = pcor_panel_y), 
                                diag = list(continuous = wrap(ggally_barDiag, binwidth = 0.04))) + theme_bw()

ggsave("../analysis/chc_wisn_ratio_corrs.png", chc_wisn_ratio_corrs, device = 'png', dpi = 300, width = 12, height = 12)
```


``````{r RHS-WISN post-analysis @Siddhesh}
#Sanctioning-WISN Lin's correlations
nurse_phc_sanc <- DescTools::CCC(wisn.states$NURSE_PHC_R_S, wisn.states$NURSE_PHC_R_WISN, na.rm = T)
doc_phc_sanc <- DescTools::CCC(wisn.states$DOC_PHC_R_S, wisn.states$DOC_PHC_R_WISN, na.rm = T)
nurse_chc_sanc <- DescTools::CCC(wisn.states$NURSE_CHC_R_S, wisn.states$NURSE_CHC_R_WISN, na.rm = T)
gdmo_chc_sanc <- DescTools::CCC(wisn.states$GDMO_AL_CHC_R_S, wisn.states$GDMO_AL_CHC_R_WISN, na.rm = T)
phys_chc_sanc <- DescTools::CCC(wisn.states$PHY_CHC_R_S, wisn.states$PHY_CHC_R_WISN, na.rm = T)
surg_chc_sanc <- DescTools::CCC(wisn.states$SUR_CHC_R_S, wisn.states$SUR_CHC_R_WISN, na.rm = T)
obgyn_chc_sanc <- DescTools::CCC(wisn.states$OBGY_CHC_R_S, wisn.states$OBGY_CHC_R_WISN, na.rm = T)
paed_chc_sanc <- DescTools::CCC(wisn.states$PAED_CHC_R_S, wisn.states$PAED_CHC_R_WISN, na.rm = T)

df.ccc <- data.frame(check.names = F,
  'Centre-Cadre Combination' = c('PHC-Nurses', 'PHC-Doctors', 'CHC-Nurses', 'CHC-GDMOs', 
                     'CHC-Physicians', 'CHC-Surgeons', 'CHC-OBGYNs', 'CHC-Paediatricians'),
  'N' = c(nrow(nurse_phc_sanc$blalt), nrow(doc_phc_sanc$blalt), nrow(nurse_chc_sanc$blalt), 
          nrow(gdmo_chc_sanc$blalt), nrow(phys_chc_sanc$blalt), nrow(surg_chc_sanc$blalt),
          nrow(obgyn_chc_sanc$blalt), nrow(paed_chc_sanc$blalt)),
  'R_C [95% CI]' = c(paste0(round(nurse_phc_sanc$rho.c$est, 2),' [',round(nurse_phc_sanc$rho.c$lwr.ci, 2),", ",round(nurse_phc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(doc_phc_sanc$rho.c$est, 2),' [',round(doc_phc_sanc$rho.c$lwr.ci, 2),", ",round(doc_phc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(nurse_chc_sanc$rho.c$est, 2),' [',round(nurse_chc_sanc$rho.c$lwr.ci, 2),", ",round(nurse_chc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(gdmo_chc_sanc$rho.c$est, 2),' [',round(gdmo_chc_sanc$rho.c$lwr.ci, 2),", ",round(gdmo_chc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(phys_chc_sanc$rho.c$est, 2),' [',round(phys_chc_sanc$rho.c$lwr.ci, 2),", ",round(phys_chc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(surg_chc_sanc$rho.c$est, 2),' [',round(surg_chc_sanc$rho.c$lwr.ci, 2),", ",round(surg_chc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(obgyn_chc_sanc$rho.c$est, 2),' [',round(obgyn_chc_sanc$rho.c$lwr.ci, 2),", ",round(obgyn_chc_sanc$rho.c$upr.ci, 2),"]"),
                     paste0(round(paed_chc_sanc$rho.c$est, 2),' [',round(paed_chc_sanc$rho.c$lwr.ci, 2),", ",round(paed_chc_sanc$rho.c$upr.ci, 2),"]")), 
  "Bias Correction Factor" = c(round(nurse_phc_sanc$C.b, 2), round(doc_phc_sanc$C.b, 2), 
                               round(nurse_chc_sanc$C.b, 2), round(gdmo_chc_sanc$C.b, 2),
                               round(phys_chc_sanc$C.b, 2), round(surg_chc_sanc$C.b, 2), 
                               round(obgyn_chc_sanc$C.b, 2), round(paed_chc_sanc$C.b, 2)))

write.csv(df.ccc, "../analysis/df_ccc_sanc_wisn.csv")
```

``````{r previous extra @Siddhesh}
phc_nurse <- ggscatter(wisn.states, x = 'NURSE_PHC_R_S_WISN_diff_per_centre', y = 'NURSE_PHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for PHC-Nurses', ylab = 'WISN Diff. per-centre for PHC-Nurses', color = 'red3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho', label.x = -1, label.y = -2) + theme_bw()

phc_doc <- ggscatter(wisn.states, x = 'DOC_PHC_R_S_WISN_diff_per_centre', y = 'DOC_PHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for PHC-Doctors', ylab = 'WISN Diff. per-centre for PHC-Doctors', color = 'red3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

chc_nurse <- ggscatter(wisn.states, x = 'NURSE_CHC_R_S_WISN_diff_per_centre', y = 'NURSE_CHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for CHC-Nurses', ylab = 'WISN Diff. per-centre for CHC-Nurses', color = 'blue3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

chc_gdmo <- ggscatter(wisn.states, x = 'GDMO_AL_CHC_R_S_WISN_diff_per_centre', y = 'GDMO_AL_CHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for CHC-GDMOs', ylab = 'WISN Diff. per-centre for CHC-GDMOs', color = 'blue3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

chc_phys <- ggscatter(wisn.states, x = 'PHY_CHC_R_S_WISN_diff_per_centre', y = 'PHY_CHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for CHC-Physicians', ylab = 'WISN Diff. per-centre for CHC-Physicians', color = 'blue3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

chc_surg <- ggscatter(wisn.states, x = 'SUR_CHC_R_S_WISN_diff_per_centre', y = 'SUR_CHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for CHC-Surgeons', ylab = 'WISN Diff. per-centre for CHC-Surgeons', color = 'blue3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

chc_obgyn <- ggscatter(wisn.states, x = 'OBGY_CHC_R_S_WISN_diff_per_centre', y = 'OBGY_CHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for CHC-OBGYNs', ylab = 'WISN Diff. per-centre for CHC-OBGYNs', color = 'blue3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

chc_paed <- ggscatter(wisn.states, x = 'PAED_CHC_R_S_WISN_diff_per_centre', y = 'PAED_CHC_R_P_WISN_diff_per_centre', xlab = 'Sanctioning Diff. per-centre for CHC-Paediatricians', ylab = 'WISN Diff. per-centre for CHC-Paeditricians', color = 'blue3') + stat_cor(method = "spearman", r.accuracy = 0.01, p.accuracy = 0.001, p.digits = 3, r.digits = 3, cor.coef.name = 'rho') + theme_bw()

sanc_diff_corr_panel <- cowplot::plot_grid(phc_nurse, phc_doc, 
                                     chc_nurse, chc_gdmo, 
                                     chc_phys, chc_surg, 
                                     chc_obgyn, chc_paed, labels = "AUTO", nrow = 2)

ggsave("../analysis/sanc_WISN_diff_corr_panel.png", sanc_diff_corr_panel, device = 'png', 
       dpi = 300, width = 15, height = 8)

```

